\chapter{Introduction}
\label{ch:introduction}

\section{Importance of continuous Development in
  Mobile Communication Technologies}

Mobile communication systems became so ubiquitous that most of our daily
use of information technology simply would not work without them.
In many first world countries, one has to almost search for places without
mobile cell network coverage and in third world countries the availability of
mobile communication is often better then the one of fresh water. \\

Because of their high availability, computer networks became so closely
incorporated in many applications, that the user experience of using those
application highly depends on a low latency and high bandwidth link
to a server providing data or even doing the actual task.
Therefor it is of essential importance, that
the performance of computer networks continuous \cite{web_content_delivery}
to grow exponentially at least as fast as other key factors like
\gls{CPU} speeds and memory capacities. \\

\acrshort{CMOS} technology and thereby digital signal processing capabilities
develops according to Moore's Law, while this is very unclear for analog
circuits in near future as stated in \cite{belgium}.
Therefor a trend to move processing steps from analog to digital
domain exists. \\

\section{Role of 60 GHz}
Since it won't be possible to increase the throughput of digital communication
systems forever by improving the \gls{SNR} as well as coding, channel allocation
and modulation schemes, the only way will be to increase the channel bandwidth.
While \gls{VHF} and \gls{UHF} bands are heavily used by many different
users and because implementation constraints require the channel
bandwidth to be small compared to the absolute carrier frequency,
the only way will be to use higher frequency bands. \\

Therefor this work experiments with the possibilities of the 60 GHz
\gls{ISM} band where the available setup allows for bandwidth of up to
1.8 GHz and therefor data rates up to 7.2 Gbit/s. \\

Such high data rates allow for new applications which simply were not possible
using existing wireless standards. Network storage devices can be accessed
at close distance with their full hard disk speed to provide fast file
up- and downloads. \gls{HD} video can be streamed lossless and uncompressed
over the air possibly replacing existing cable connections to video
projectors and monitors. \\

60 GHz confronts engineers with many new design constraints though. The very
high free-space path loss requires for advanced beam forming methods
for distances above a few meters.
This is not only possible using huge scale parabolic
antennas as it is done for satellite networks for decades, but can also
be done in a much more dynamic way by means of antenna arrays.
The very small wave length allows to integrate these arrays
directly on an \gls{IC}. \\

On the other hand, the high attenuation allows to reuse the same channel
in a relatively close cell. \\

While the object sizes and distances in an indoor environment stay the same,
the symbol rates on 60 GHz get much higher. Therefor the resulting
delay spread is wider and correct channel estimation and correction
gains in complexity.  \\

\section{This Thesis}
In order to analyze the different receiver designs,
to get measurements of channel characteristics,
to quantify phase noise figures and finally to find
performance limiting impairments on 60 GHz communication
systems, a versatile communication system was needed. \\

Therefor different receiver architectures were analyzed as described in
\chapref{chap:rx}. A communication system including mod- and demodulation,
pulse shaping, time and frequency synchronization as well as channel and phase noise
estimation and correction was implemented in software as described in
\chapref{chap:sys}.
\chapref{chap:fpga} describes the \gls{FPGA} design, which was developed
to interface a 3.6 GS/s \gls{ADC},
store it's data in real time, provide a fast download interface and thereby
to allow reproduction of simulation results on real hardware.
All the used \gls{RF} components were measured using a state of the art
vector network analyzer as noted in \chapref{chap:comp}.
Finally \chapref{chap:res_450} contains information
about the exact test setup and the achieved performance of the system. \\

%%  LocalWords:  interferer rx CMOS SNR Gbit HD lossless IC sys fpga
%%  LocalWords:  FPGA Moore's
